Compiling refinement types to dependent types

### 2020-07-19 tex/paper.tex
Use \ranchor instead of \ottdrulename
Start defining term translation

Before we dive into defining these functions, $\tranderiv$ deserves a few introductory words.
Although the aim is to translate terms,
what this function really does is translating the surface typing derivation for a given (well-typed) term
into a typing derivation in the core language.
The reason for the extra complexity stems from the \ottdrulename{T-Sub} typing rule.
In particular, this rule invokes the subtyping check, which, in turn, invokes the oracle.
The oracle then might produce a core language term proving that the subtyping relation in question holds,
and the presence of this rule is in some sense a carrier of this proof term.

@@

\paragraph{Terms.}
Finally we define $\tranterm$:
\begin{equation}
\begin{aligned}
  & \tranterm(x) &&
    \triangleq x                                                              \\
  & \tranterm(\lambda x : \nonterm{ts}. \nonterm{es})  &&
    \triangleq \lambda x : \tranty(\nonterm{ts}). \tranterm(\nonterm{es})     \\
  & \tranterm(\nonterm{es}_1 \nonterm{es}_2)  &&
    \triangleq \tranterm(\nonterm{es}_1) \tranterm(\nonterm{es}_2)            \\
\end{aligned}
\end{equation}

>>>>

Before we dive into defining these functions, $\tranderiv$ deserves a few introductory words.
Although the aim is to translate terms,
what this function really does is translating the surface typing derivation for a given (well-typed) term
into a typing derivation in the core language.
The reason for the extra complexity stems from the \ranchor{T-Sub} typing rule.
In particular, this rule invokes the subtyping check, which, in turn, invokes the oracle.
The oracle then might produce a core language term proving that the subtyping relation in question holds,
and the presence of this rule is in some sense a carrier of this proof term.

@@

\paragraph{Terms.}
Finally we define $\tranderiv$.
As it is defined on typing derivation trees,
we consider the term typing rule that is used last to prove $\nonterm G \vdash \nonterm{es} : \nonterm{ts}$.

\begin{itemize}
  \item \ranchor{T-Unit}.
    This rule has no premises, so we just translate it into \ranchor{CT-UnitTerm}:
    \[
      \inferrule{ }{\nonterm G \vdash \unit : \{ \gterm v : \Unit | \top \}} \longmapsto \inferrule{ }{\nonterm{GC} \vdash \unitc : \Unitc}
    \]
\end{itemize}

\begin{equation}
\begin{aligned}
  & \tranterm(x) &&
    \triangleq x                                                              \\
  & \tranterm(\lambda x : \nonterm{ts}. \nonterm{es})  &&
    \triangleq \lambda x : \tranty(\nonterm{ts}). \tranterm(\nonterm{es})     \\
  & \tranterm(\nonterm{es}_1 \nonterm{es}_2)  &&
    \triangleq \tranterm(\nonterm{es}_1) \tranterm(\nonterm{es}_2)            \\
\end{aligned}
\end{equation}
